%-------------------------
% Resume in Latex
% Author : Yiran Cao
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Yiran (Aurora) Cao} & Email : \href{mailto:cao.805@osu.edu}{cao.805@osu.edu}\\
   & Mobile : +1-614-446-7207 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Ohio State University}{Columbus, OH}
      {Master of Science in Computer Science and Engineering;  GPA: 3.625}{Aug. 2016 -- Present}
      \resumeItemListStart
       \resumeItem{Courses Taken: }
          {Advanced Algorithms(A), Operating Systems(A)}
       \resumeItem{Courses Taking: }
          {Machine Learning, Data Mining, Data Visualization, Foundations of Programming Language}
      \resumeItemListEnd
    \resumeSubheading
      {Renmin University of China}{Beijing, China}
      {Bachelor of Engineering in Computer Science;  GPA: 3.45}{Sept. 2012 -- Jun. 2016}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Linear Models and SGD on Brain Image Data}{}
      {Machine Learning Project}{Mar 2017}
      \resumeItemListStart
        \resumeItem{}
          {Analyzed 3D brain images to predict whether a person is looking at a picture or a sentence.  \href{https://github.com/wanderlustyc/linear-model}{\underline{source code}}}
        \resumeItem{}
          {Implemented SVM in python, using stochastic gradient descent for hinge loss and logistic loss}
        \resumeItem{}{Obtained an accuracy of 85.29\% on test set}
      \resumeItemListEnd

    \resumeSubheading
      {k-NN Classifier Implementation and Application}{}
      {Data Mining Project}{Feb 2017}
      \resumeItemListStart
        \resumeItem{}
          {Implemented a k-NN classifier in R to predict people’s income. \href{https://github.com/wanderlustyc/k-NN}{\underline{source code}}}
        \resumeItem{}
          {Used dataset with 52 mixed types of attributes.}
        \resumeItem{}
          {Obtained an accuracy of 87.9\%, better than the off-the-shelf $kknn$ classifier in R.}
      \resumeItemListEnd

    \resumeSubheading
      {Lisp Interpreter}{}
      {Programming Language Project}{Feb 2017 - Mar 2017}
      \resumeItemListStart
        \resumeItem{}
          {Implemented a Lisp interpreter in Java. \href{https://github.com/wanderlustyc/LISP-Interpreter}{\underline{source code}} }
        \resumeItem{}
          {Implemented the input, evaluation and output stage of Lisp on top of a recursive descent parser.}
        \resumeItem{}
          {Support user-defined function evaluation.}
      \resumeItemListEnd

    \resumeSubheading
      {A Critic and Redesign of Visualizations in \textit{A Network Framework of Cultural History}}{}
      {Data Visualization}{Mar 2017}
      \resumeItemListStart
        \resumeItem{}
          {\textit{A Network Framework of Cultural History} is an interesting paper published on \textit{Science}.}
        \resumeItem{}
          {Criticized data visualizations in the paper from the perspective of graphical semiology.}
        \resumeItem{}
          {Redesigned some of the visualizations using D3.js. \href{https://github.com/wanderlustyc/DVRedesign}{\underline{source code}}}
      \resumeItemListEnd

    \resumeSubheading
      {Quora Question Pairs Challenge}{}
      {Kaggle Competition}{In Progress}
      \resumeItemListStart
        \resumeItem{}
          {To predict whether a provided pair of questions contain two questions with the same meaning. }
        \resumeItem{}
          {Exploring NLP techniques to apply to this problem.}
      \resumeItemListEnd

    

  \resumeSubHeadingListEnd


%-----------EMPLOYMENTS-----------------
\section{Employments}


  
  \resumeSubHeadingListStart
  \resumeSubheading
  {Qunar.com}{Beijing, China}
  {Data Analyst Intern}{Apr 15 - Aug 15}
    \resumeItemListStart
      \resumeItem{}
        {Analyzed data of hotel transactions, to access sales performance and to help make appropriate policies.}
      \resumeItem{}
        {Extracted raw data in Hive with SQL.}
      \resumeItem{}
        {Analyzed and visualized data with R, and wrote weekly and monthly data analysis report.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%
% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Java, C, Python, Javascript}
   }
   \item{
    \textbf{Data Analysis}{: R, D3.js}
   }
   \item{
     \textbf{Web}{: Bootstrap, jQuery, Node JS}
   }
   \item{
    \textbf{Operating Systems}{: Linux, Windows, Mac OSX}
   }
   \item{
    \textbf{Databases}{: MySQL, PostgreSQL}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
